H3 Supplement

### 2023-02-10 supp_H3.Rmd
heat maps and flag plots added

---
title: "H2 Supplement"
author: "Mariola Paruzel-Czachura, Cillian McHugh"
date: "`r format(Sys.time(), '%d %B, %Y')`"
bibliography: "resources/bib/My Library.bib"
csl: "resources/bib/apa.csl"
output:
  bookdown::html_document2:
    fig_caption: yes
    toc: true
    toc_float:
      toc_collapsed: false
    toc_depth: 4
    number_sections: false
editor_options: 
  chunk_output_type: console
---

@@

```{r}
rm(list = ls())
library(tidyverse)
library(plyr)
library(psych)
library(skimr)
library(corrplot)
library(Hmisc)
#library(psy)
library(afex)
#devtools::install_github("cillianmiltown/R_desnum")
library(desnum)
library(papaja)
library(purrr)
#install.packages("interactions")
library(interactions)
library(kableExtra)
#devtools::install_github("crsh/papaja")
library("papaja")
library(lme4)
library(car)
library(ggplot2)
library(nlme)
#install.packages("reshape")
library(reshape)
library(corx)
library(lsr)
#install.packages("Cairo")
#library(Cairo)
library(foreign)
library(ltm)
library("ggpubr")
#install.packages("rworldmap")
library(rworldmap)
#devtools::install_github("rensa/ggflags")
library(ggflags)
#devtools::install_github("schliebs/ggoxford")
library(ggoxford)
library(ggforce)
library(ggbeeswarm)
library(countrycode)
```

@@

>>>>

---
title: "H3 Supplement"
author: "Mariola Paruzel-Czachura, Cillian McHugh"
date: "`r format(Sys.time(), '%d %B, %Y')`"
bibliography: "resources/bib/My Library.bib"
csl: "resources/bib/apa.csl"
output:
  bookdown::html_document2:
    fig_caption: yes
    toc: true
    toc_float:
      toc_collapsed: false
    toc_depth: 4
    number_sections: false
editor_options: 
  chunk_output_type: console
---

@@

```{r}
rm(list = ls())
library(tidyverse)
library(plyr)
library(psych)
library(skimr)
library(corrplot)
library(Hmisc)
#library(psy)
library(afex)
#devtools::install_github("cillianmiltown/R_desnum")
library(desnum)
library(papaja)
library(purrr)
#install.packages("interactions")
library(interactions)
library(kableExtra)
#devtools::install_github("crsh/papaja")
library("papaja")
library(lme4)
library(car)
library(ggplot2)
library(nlme)
#install.packages("reshape")
library(reshape)
library(corx)
library(lsr)
#install.packages("Cairo")
#library(Cairo)
library(foreign)
library(ltm)
library("ggpubr")
#install.packages("rworldmap")
library(rworldmap)
#install.packages("grConvert")
#devtools::install_github("sjp/grConvert")
library(grConvert)
#remove.packages("grImport2")
#install.packages("grImport2")
library(grImport2)
#install.packages("ragg")
#remove.packages("ggflags")
#install.packages("devtools")
#devtools::install_github("jimjam-slam/ggflags", force = TRUE)
#help("install_github")
#devtools::install_github("rensa/ggflags", force = TRUE, dependencies = TRUE)
library(ggflags)
#devtools::install_github("schliebs/ggoxford")
library(ggoxford)
library(ggforce)
library(ggbeeswarm)
library(countrycode)

source('modify_flags.R')

```

@@

## Power Distance
## Power Distance

```{r}
x <- df

x <- x[which(is.na(x$Power.Distance)==FALSE),]

x$ISO2 <- countrycode(x$ISO3, "iso3c", "iso2c")
x$iso2 <- tolower(x$ISO2)

x <- x %>% group_by(iso2) %>% do(data = (.)) %>% with( set_names(data, iso2) )

means_fun <- function(x){
  mean(x$moral_identity_symbolic,na.rm = T)
}
symbolic_means <- lapply(x, means_fun)
sd_fun <- function(x){
  sd(x$moral_identity_symbolic,na.rm = T)
}
symbolic_sds <- lapply(x, sd_fun)
N_fun <- function(x){
  length(x$sex3)
}
Ns <- lapply(x, N_fun)

power_means_fun <- function(x){
  mean(x$Power.Distance)
}
power_score <- lapply(x, power_means_fun)
x$Ukraine$Power.Distance

test <- 
  cbind.data.frame(
     round(do.call(rbind, symbolic_means),digits=2)
    ,round(do.call(rbind, symbolic_sds),digits=2)
    ,round(do.call(rbind, power_score),digits=2)
    ,round(do.call(rbind, Ns),digits=2)
    )

test <- `colnames<-`(test, c("symbolic_means","symbolic_sds","power_score", "Ns"))
test$iso2c <- rownames(test)
#autocoup_df$iso2c <- countrycode(test$country, "country.name", "iso2c")
# test$iso2c <- countrycode(test$country, "country.name", "iso2c")
# test$iso2c <- tolower(test$iso2c)
test$country <- countrycode(test$iso2c, "iso2c", "country.name")

test
```

h1 <- .3
w1 <- .5
s1 <- 18

lm_fit_intercept <- lm(moral_identity_symbolic ~ Power.Distance, data = df)

lm_fit <- lm(moral_identity_symbolic ~
                    # sex3
                    # + age
                     Power.Distance
                    + Individualism
                    + Masculinity
                    + Uncertainty.Avoidance
                    + Long.Term.Orientation
                    + Indulgence
                    + CTL_DG
                    + CTL_DS
                    + CTL_C
                , data = df
            )
lm_fit$coefficients

lm_fit$coefficients[1]
lm_fit$coefficients[2]

g1 <- ggplot(test, aes(power_score
                       ,symbolic_means
                       ,country=iso2c
                       #,size=Ns
))+
  geom_abline(slope=lm_fit_intercept$coefficients[2],
              #slope=lm_fit$coefficients[2],
              intercept=lm_fit_intercept$coefficients[1],
              color="darkgrey",
              size=.5)+
  #geom_point(size=13,color="black")+
  geom_flag(
    position=position_jitter(
      h = h1
      , w = w1
      , seed = s1)
    #aes(power_score,symbolic_means,country = iso2c#, size=1#(Ns)
    #)
    ,size=7.5
  )+
  scale_country()+
  #scale_size(range = c(8,10))+
  geom_text(aes(power_score,symbolic_means),label=test$country
            ,vjust=3.8
            ,hjust=.44
            #,nudge_x = .03
            ,size = 1.6
            #,check_overlap = TRUE
            ,position = position_jitter(
              h = h1
              , w = w1
              , seed = s1
            )
  )+
  xlab("Power Distance")+
  ylab("Symbolization")+
  scale_y_continuous(expand = c(0, 0), limits = c(0, 10))+
  theme_bw() +
  theme(panel.border = element_blank(),
        axis.line = element_line(size = .2),
        strip.background  = element_blank(),
        #panel.grid = element_blank(),
        plot.title=element_text(#family="Times",
          size=12
        ),
        #legend.position="right",
        legend.text=element_text(#family="Times",
          size=8
        ),
        legend.title=element_text(#family="Times",
          size=10
        ),
        axis.text=element_text(#family="Times",
          colour = "black",
          size=8
        ),
        axis.ticks.x = element_blank(),
        axis.title=element_text(#family="Times",
          size=12
        ),
        strip.text=element_text(#family = "Times",
          size = 12
        ),
        # strip.background = element_rect(fill = "white"),
        legend.position="none")

ggsave("plots/power_symbolization.png", g1, width = 10, height = 6, units = "in", dpi = 300)

```

```{r, Symbolizationpower,fig.cap="Relationship between Power Diatance and Symbolization",include=TRUE}
suppressWarnings(print(g1))

```

## Individualism

```{r}
x <- df
x$Individualism
x <- x[which(is.na(x$Individualism)==FALSE),]

x$ISO2 <- countrycode(x$ISO3, "iso3c", "iso2c")
x$iso2 <- tolower(x$ISO2)

x <- x %>% group_by(iso2) %>% do(data = (.)) %>% with( set_names(data, iso2) )

means_fun <- function(x){
  mean(x$moral_identity_symbolic,na.rm = T)
}
symbolic_means <- lapply(x, means_fun)
sd_fun <- function(x){
  sd(x$moral_identity_symbolic,na.rm = T)
}
symbolic_sds <- lapply(x, sd_fun)
N_fun <- function(x){
  length(x$sex3)
}
Ns <- lapply(x, N_fun)

power_means_fun <- function(x){
  mean(x$Individualism)
}
power_score <- lapply(x, power_means_fun)
x$Ukraine$Power.Distance

test <- 
  cbind.data.frame(
     round(do.call(rbind, symbolic_means),digits=2)
    ,round(do.call(rbind, symbolic_sds),digits=2)
    ,round(do.call(rbind, power_score),digits=2)
    ,round(do.call(rbind, Ns),digits=2)
    )

test <- `colnames<-`(test, c("symbolic_means","symbolic_sds","power_score", "Ns"))
test$iso2c <- rownames(test)
#autocoup_df$iso2c <- countrycode(test$country, "country.name", "iso2c")
# test$iso2c <- countrycode(test$country, "country.name", "iso2c")
# test$iso2c <- tolower(test$iso2c)
test$country <- countrycode(test$iso2c, "iso2c", "country.name")

test
```

h1 <- .3
w1 <- .5
s1 <- 18

lm_fit_intercept <- lm(moral_identity_symbolic ~ Individualism, data = df)

lm_fit <- lm(moral_identity_symbolic ~
                    # sex3
                    # + age
                     Power.Distance
                    + Individualism
                    + Masculinity
                    + Uncertainty.Avoidance
                    + Long.Term.Orientation
                    + Indulgence
                    + CTL_DG
                    + CTL_DS
                    + CTL_C
                , data = df
            )

lm_fit$coefficients[1]
lm_fit$coefficients[3]

g1 <- ggplot(test, aes(power_score
                       ,symbolic_means
                       ,country=iso2c
                       #,size=Ns
))+
  geom_abline(slope=lm_fit_intercept$coefficients[2],
              #slope=lm_fit$coefficients[3],
              intercept=lm_fit_intercept$coefficients[1],
              color="darkgrey",
              size=.5)+
  #geom_point(size=13,color="black")+
  geom_flag(
    position=position_jitter(
      h = h1
      , w = w1
      , seed = s1)
    #aes(power_score,symbolic_means,country = iso2c#, size=1#(Ns)
    #)
    ,size=7.5
  )+
  scale_country()+
  #scale_size(range = c(8,10))+
  geom_text(aes(power_score,symbolic_means),label=test$country
            ,vjust=3.8
            ,hjust=.44
            #,nudge_x = .03
            ,size = 1.6
            #,check_overlap = TRUE
            ,position = position_jitter(
              h = h1
              , w = w1
              , seed = s1
            )
  )+
  xlab("Individualism")+
  ylab("Symbolization")+
  scale_y_continuous(expand = c(0, 0), limits = c(0, 10))+
  theme_bw() +
  theme(panel.border = element_blank(),
        axis.line = element_line(size = .2),
        strip.background  = element_blank(),
        #panel.grid = element_blank(),
        plot.title=element_text(#family="Times",
          size=12
        ),
        #legend.position="right",
        legend.text=element_text(#family="Times",
          size=8
        ),
        legend.title=element_text(#family="Times",
          size=10
        ),
        axis.text=element_text(#family="Times",
          colour = "black",
          size=8
        ),
        axis.ticks.x = element_blank(),
        axis.title=element_text(#family="Times",
          size=12
        ),
        strip.text=element_text(#family = "Times",
          size = 12
        ),
        # strip.background = element_rect(fill = "white"),
        legend.position="none")

ggsave("plots/individualism_symbolization.png", g1, width = 10, height = 6, units = "in", dpi = 300)

```

```{r, SymbolizationIndividualism,fig.cap="Relationship between Individualism and Symbolization",include=TRUE}
suppressWarnings(print(g1))

```

## Masculinity

```{r}
x <- df

df$Uncertainty.Avoidance
x <- x[which(is.na(x$Masculinity)==FALSE),]

x$ISO2 <- countrycode(x$ISO3, "iso3c", "iso2c")
x$iso2 <- tolower(x$ISO2)

x <- x %>% group_by(iso2) %>% do(data = (.)) %>% with( set_names(data, iso2) )

means_fun <- function(x){
  mean(x$moral_identity_symbolic,na.rm = T)
}
symbolic_means <- lapply(x, means_fun)
sd_fun <- function(x){
  sd(x$moral_identity_symbolic,na.rm = T)
}
symbolic_sds <- lapply(x, sd_fun)
N_fun <- function(x){
  length(x$sex3)
}
Ns <- lapply(x, N_fun)

power_means_fun <- function(x){
  mean(x$Masculinity)
}
power_score <- lapply(x, power_means_fun)
x$Ukraine$Uncertainty.Avoidance

test <- 
  cbind.data.frame(
     round(do.call(rbind, symbolic_means),digits=2)
    ,round(do.call(rbind, symbolic_sds),digits=2)
    ,round(do.call(rbind, power_score),digits=2)
    ,round(do.call(rbind, Ns),digits=2)
    )

test <- `colnames<-`(test, c("symbolic_means","symbolic_sds","power_score", "Ns"))
test$iso2c <- rownames(test)
#autocoup_df$iso2c <- countrycode(test$country, "country.name", "iso2c")
# test$iso2c <- countrycode(test$country, "country.name", "iso2c")
# test$iso2c <- tolower(test$iso2c)
test$country <- countrycode(test$iso2c, "iso2c", "country.name")

test
```

h1 <- .3
w1 <- .5
s1 <- 18

lm_fit_intercept <- lm(moral_identity_symbolic ~ Masculinity, data = df)

lm_fit <- lm(moral_identity_symbolic ~
                    # sex3
                    # + age
                     Power.Distance
                    + Individualism
                    + Masculinity
                    + Uncertainty.Avoidance
                    + Long.Term.Orientation
                    + Indulgence
                    + CTL_DG
                    + CTL_DS
                    + CTL_C
                , data = df
            )

lm_fit$coefficients[1]
lm_fit$coefficients[2]

g1 <- ggplot(test, aes(power_score
                       ,symbolic_means
                       ,country=iso2c
                       #,size=Ns
))+
  geom_abline(slope=lm_fit_intercept$coefficients[2],
              #slope=lm_fit$coefficients[5],
              intercept=lm_fit_intercept$coefficients[1],
              color="darkgrey",
              size=.5)+
  #geom_point(size=13,color="black")+
  geom_flag(
    position=position_jitter(
      h = h1
      , w = w1
      , seed = s1)
    #aes(power_score,symbolic_means,country = iso2c#, size=1#(Ns)
    #)
    ,size=7.5
  )+
  scale_country()+
  #scale_size(range = c(8,10))+
  geom_text(aes(power_score,symbolic_means),label=test$country
            ,vjust=3.8
            ,hjust=.44
            #,nudge_x = .03
            ,size = 1.6
            #,check_overlap = TRUE
            ,position = position_jitter(
              h = h1
              , w = w1
              , seed = s1
            )
  )+
  xlab("Masculinity")+
  ylab("Symbolization")+
  scale_y_continuous(expand = c(0, 0), limits = c(0, 10))+
  theme_bw() +
  theme(panel.border = element_blank(),
        axis.line = element_line(size = .2),
        strip.background  = element_blank(),
        #panel.grid = element_blank(),
        plot.title=element_text(#family="Times",
          size=12
        ),
        #legend.position="right",
        legend.text=element_text(#family="Times",
          size=8
        ),
        legend.title=element_text(#family="Times",
          size=10
        ),
        axis.text=element_text(#family="Times",
          colour = "black",
          size=8
        ),
        axis.ticks.x = element_blank(),
        axis.title=element_text(#family="Times",
          size=12
        ),
        strip.text=element_text(#family = "Times",
          size = 12
        ),
        # strip.background = element_rect(fill = "white"),
        legend.position="none")

ggsave("plots/masc_symbolization.png", g1, width = 10, height = 6, units = "in", dpi = 300)

```

```{r, SymbolizationMasc,fig.cap="Relationship between Masculinity and Symbolization",include=TRUE}
suppressWarnings(print(g1))

```

## Long Term Orientation

```{r}
x <- df

x$Long.Term.Orientation
x <- x[which(is.na(x$Long.Term.Orientation)==FALSE),]

x$ISO2 <- countrycode(x$ISO3, "iso3c", "iso2c")
x$iso2 <- tolower(x$ISO2)

x <- x %>% group_by(iso2) %>% do(data = (.)) %>% with( set_names(data, iso2) )

means_fun <- function(x){
  mean(x$moral_identity_symbolic,na.rm = T)
}
symbolic_means <- lapply(x, means_fun)
sd_fun <- function(x){
  sd(x$moral_identity_symbolic,na.rm = T)
}
symbolic_sds <- lapply(x, sd_fun)
N_fun <- function(x){
  length(x$sex3)
}
Ns <- lapply(x, N_fun)

power_means_fun <- function(x){
  mean(x$Long.Term.Orientation)
}
power_score <- lapply(x, power_means_fun)
x$Ukraine$Long.Term.Orientation

test <- 
  cbind.data.frame(
     round(do.call(rbind, symbolic_means),digits=2)
    ,round(do.call(rbind, symbolic_sds),digits=2)
    ,round(do.call(rbind, power_score),digits=2)
    ,round(do.call(rbind, Ns),digits=2)
    )

test <- `colnames<-`(test, c("symbolic_means","symbolic_sds","power_score", "Ns"))
test$iso2c <- rownames(test)
#autocoup_df$iso2c <- countrycode(test$country, "country.name", "iso2c")
# test$iso2c <- countrycode(test$country, "country.name", "iso2c")
# test$iso2c <- tolower(test$iso2c)
test$country <- countrycode(test$iso2c, "iso2c", "country.name")

test
```

h1 <- .3
w1 <- .5
s1 <- 18

lm_fit_intercept <- lm(moral_identity_symbolic ~ Long.Term.Orientation, data = df)

lm_fit <- lm(moral_identity_symbolic ~
                    # sex3
                    # + age
                     Power.Distance
                    + Individualism
                    + Masculinity
                    + Uncertainty.Avoidance
                    + Long.Term.Orientation
                    + Indulgence
                    + CTL_DG
                    + CTL_DS
                    + CTL_C
                , data = df
            )

lm_fit
lm_fit$coefficients[1]
lm_fit$coefficients[6]

g1 <- ggplot(test, aes(power_score
                       ,symbolic_means
                       ,country=iso2c
                       #,size=Ns
))+
  geom_abline(slope=lm_fit_intercept$coefficients[2],
              #slope=lm_fit$coefficients[6],
              intercept=lm_fit_intercept$coefficients[1],
              color="darkgrey",
              size=.5)+
  #geom_point(size=13,color="black")+
  geom_flag(
    position=position_jitter(
      h = h1
      , w = w1
      , seed = s1)
    #aes(power_score,symbolic_means,country = iso2c#, size=1#(Ns)
    #)
    ,size=7.5
  )+
  scale_country()+
  #scale_size(range = c(8,10))+
  geom_text(aes(power_score,symbolic_means),label=test$country
            ,vjust=3.8
            ,hjust=.44
            #,nudge_x = .03
            ,size = 1.6
            #,check_overlap = TRUE
            ,position = position_jitter(
              h = h1
              , w = w1
              , seed = s1
            )
  )+
  xlab("Long Term Orientation")+
  ylab("Symbolization")+
  scale_y_continuous(expand = c(0, 0), limits = c(0, 10))+
  theme_bw() +
  theme(panel.border = element_blank(),
        axis.line = element_line(size = .2),
        strip.background  = element_blank(),
        #panel.grid = element_blank(),
        plot.title=element_text(#family="Times",
          size=12
        ),
        #legend.position="right",
        legend.text=element_text(#family="Times",
          size=8
        ),
        legend.title=element_text(#family="Times",
          size=10
        ),
        axis.text=element_text(#family="Times",
          colour = "black",
          size=8
        ),
        axis.ticks.x = element_blank(),
        axis.title=element_text(#family="Times",
          size=12
        ),
        strip.text=element_text(#family = "Times",
          size = 12
        ),
        # strip.background = element_rect(fill = "white"),
        legend.position="none")

ggsave("plots/LTO_symbolization.png", g1, width = 10, height = 6, units = "in", dpi = 300)

```

```{r, SymbolizationLTO,fig.cap="Relationship between Long Term Orientation and Symbolization",include=TRUE}
suppressWarnings(print(g1))

```

## Indulgence

```{r}
x <- df
x$Indulgence
x <- x[which(is.na(x$Indulgence)==FALSE),]

x$ISO2 <- countrycode(x$ISO3, "iso3c", "iso2c")
x$iso2 <- tolower(x$ISO2)

x <- x %>% group_by(iso2) %>% do(data = (.)) %>% with( set_names(data, iso2) )

means_fun <- function(x){
  mean(x$moral_identity_symbolic,na.rm = T)
}
symbolic_means <- lapply(x, means_fun)
sd_fun <- function(x){
  sd(x$moral_identity_symbolic,na.rm = T)
}
symbolic_sds <- lapply(x, sd_fun)
N_fun <- function(x){
  length(x$sex3)
}
Ns <- lapply(x, N_fun)

power_means_fun <- function(x){
  mean(x$Indulgence)
}
power_score <- lapply(x, power_means_fun)
x$Ukraine$Indulgence

test <- 
  cbind.data.frame(
     round(do.call(rbind, symbolic_means),digits=2)
    ,round(do.call(rbind, symbolic_sds),digits=2)
    ,round(do.call(rbind, power_score),digits=2)
    ,round(do.call(rbind, Ns),digits=2)
    )

test <- `colnames<-`(test, c("symbolic_means","symbolic_sds","power_score", "Ns"))
test$iso2c <- rownames(test)
#autocoup_df$iso2c <- countrycode(test$country, "country.name", "iso2c")
# test$iso2c <- countrycode(test$country, "country.name", "iso2c")
# test$iso2c <- tolower(test$iso2c)
test$country <- countrycode(test$iso2c, "iso2c", "country.name")

test
```

h1 <- .3
w1 <- .5
s1 <- 18

lm_fit_intercept <- lm(moral_identity_symbolic ~ Indulgence, data = df)

lm_fit <- lm(moral_identity_symbolic ~
                    # sex3
                    # + age
                     Power.Distance
                    + Individualism
                    + Masculinity
                    + Uncertainty.Avoidance
                    + Long.Term.Orientation
                    + Indulgence
                    + CTL_DG
                    + CTL_DS
                    + CTL_C
                , data = df
            )

lm_fit$coefficients[1]
lm_fit$coefficients[2]

g1 <- ggplot(test, aes(power_score
                       ,symbolic_means
                       ,country=iso2c
                       #,size=Ns
))+
  geom_abline(slope=lm_fit_intercept$coefficients[2],
              #slope=lm_fit$coefficients[7],
              intercept=lm_fit_intercept$coefficients[1],
              color="darkgrey",
              size=.5)+
  #geom_point(size=13,color="black")+
  geom_flag(
    position=position_jitter(
      h = h1
      , w = w1
      , seed = s1)
    #aes(power_score,symbolic_means,country = iso2c#, size=1#(Ns)
    #)
    ,size=7.5
  )+
  scale_country()+
  #scale_size(range = c(8,10))+
  geom_text(aes(power_score,symbolic_means),label=test$country
            ,vjust=3.8
            ,hjust=.44
            #,nudge_x = .03
            ,size = 1.6
            #,check_overlap = TRUE
            ,position = position_jitter(
              h = h1
              , w = w1
              , seed = s1
            )
  )+
  xlab("Indulgence")+
  ylab("Symbolization")+
  scale_y_continuous(expand = c(0, 0), limits = c(0, 10))+
  theme_bw() +
  theme(panel.border = element_blank(),
        axis.line = element_line(size = .2),
        strip.background  = element_blank(),
        #panel.grid = element_blank(),
        plot.title=element_text(#family="Times",
          size=12
        ),
        #legend.position="right",
        legend.text=element_text(#family="Times",
          size=8
        ),
        legend.title=element_text(#family="Times",
          size=10
        ),
        axis.text=element_text(#family="Times",
          colour = "black",
          size=8
        ),
        axis.ticks.x = element_blank(),
        axis.title=element_text(#family="Times",
          size=12
        ),
        strip.text=element_text(#family = "Times",
          size = 12
        ),
        # strip.background = element_rect(fill = "white"),
        legend.position="none")

ggsave("plots/indulgence_symbolization.png", g1, width = 10, height = 6, units = "in", dpi = 300)

```

```{r, SymbolizationIndulgence,fig.cap="Relationship between Indulgence and Symbolization",include=TRUE}
suppressWarnings(print(g1))

```

## Tightness Domain General

```{r}
x <- df
x$CTL_DG
x <- x[which(is.na(x$CTL_DG)==FALSE),]

x$ISO2 <- countrycode(x$ISO3, "iso3c", "iso2c")
x$iso2 <- tolower(x$ISO2)

x <- x %>% group_by(iso2) %>% do(data = (.)) %>% with( set_names(data, iso2) )

means_fun <- function(x){
  mean(x$moral_identity_symbolic,na.rm = T)
}
symbolic_means <- lapply(x, means_fun)
sd_fun <- function(x){
  sd(x$moral_identity_symbolic,na.rm = T)
}
symbolic_sds <- lapply(x, sd_fun)
N_fun <- function(x){
  length(x$sex3)
}
Ns <- lapply(x, N_fun)

power_means_fun <- function(x){
  mean(x$CTL_DG)
}
power_score <- lapply(x, power_means_fun)
x$Ukraine$CTL_DG

test <- 
  cbind.data.frame(
     round(do.call(rbind, symbolic_means),digits=2)
    ,round(do.call(rbind, symbolic_sds),digits=2)
    ,round(do.call(rbind, power_score),digits=2)
    ,round(do.call(rbind, Ns),digits=2)
    )

test <- `colnames<-`(test, c("symbolic_means","symbolic_sds","power_score", "Ns"))
test$iso2c <- rownames(test)
#autocoup_df$iso2c <- countrycode(test$country, "country.name", "iso2c")
# test$iso2c <- countrycode(test$country, "country.name", "iso2c")
# test$iso2c <- tolower(test$iso2c)
test$country <- countrycode(test$iso2c, "iso2c", "country.name")

test
```

h1 <- .3
w1 <- .5
s1 <- 18

lm_fit_intercept <- lm(moral_identity_symbolic ~ CTL_DG, data = df)

lm_fit <- lm(moral_identity_symbolic ~
                    # sex3
                    # + age
                     Power.Distance
                    + Individualism
                    + Masculinity
                    + Uncertainty.Avoidance
                    + Long.Term.Orientation
                    + Indulgence
                    + CTL_DG
                    + CTL_DS
                    + CTL_C
                , data = df
            )

lm_fit$coefficients[1]
lm_fit$coefficients[2]

g1 <- ggplot(test, aes(power_score
                       ,symbolic_means
                       ,country=iso2c
                       #,size=Ns
))+
  geom_abline(slope=lm_fit_intercept$coefficients[2],
              #slope=lm_fit$coefficients[8],
              intercept=lm_fit_intercept$coefficients[1],
              color="darkgrey",
              size=.5)+
  #geom_point(size=13,color="black")+
  geom_flag(
    position=position_jitter(
      h = h1
      , w = w1
      , seed = s1)
    #aes(power_score,symbolic_means,country = iso2c#, size=1#(Ns)
    #)
    ,size=7.5
  )+
  scale_country()+
  #scale_size(range = c(8,10))+
  geom_text(aes(power_score,symbolic_means),label=test$country
            ,vjust=3.8
            ,hjust=.44
            #,nudge_x = .03
            ,size = 1.6
            #,check_overlap = TRUE
            ,position = position_jitter(
              h = h1
              , w = w1
              , seed = s1
            )
  )+
  xlab("Tightness: Domain General")+
  ylab("Symbolization")+
  scale_y_continuous(expand = c(0, 0), limits = c(0, 10))+
  theme_bw() +
  theme(panel.border = element_blank(),
        axis.line = element_line(size = .2),
        strip.background  = element_blank(),
        #panel.grid = element_blank(),
        plot.title=element_text(#family="Times",
          size=12
        ),
        #legend.position="right",
        legend.text=element_text(#family="Times",
          size=8
        ),
        legend.title=element_text(#family="Times",
          size=10
        ),
        axis.text=element_text(#family="Times",
          colour = "black",
          size=8
        ),
        axis.ticks.x = element_blank(),
        axis.title=element_text(#family="Times",
          size=12
        ),
        strip.text=element_text(#family = "Times",
          size = 12
        ),
        # strip.background = element_rect(fill = "white"),
        legend.position="none")

ggsave("plots/ct_dg_symbolization.png", g1, width = 10, height = 6, units = "in", dpi = 300)

```

```{r, SymbolizationTDG,fig.cap="Relationship between Domain General Tightness and Symbolization",include=TRUE}
suppressWarnings(print(g1))

```

## Tightness Domain Specific

```{r}
x <- df
x$CTL_DS
x <- x[which(is.na(x$CTL_DS)==FALSE),]

x$ISO2 <- countrycode(x$ISO3, "iso3c", "iso2c")
x$iso2 <- tolower(x$ISO2)

x <- x %>% group_by(iso2) %>% do(data = (.)) %>% with( set_names(data, iso2) )

means_fun <- function(x){
  mean(x$moral_identity_symbolic,na.rm = T)
}
symbolic_means <- lapply(x, means_fun)
sd_fun <- function(x){
  sd(x$moral_identity_symbolic,na.rm = T)
}
symbolic_sds <- lapply(x, sd_fun)
N_fun <- function(x){
  length(x$sex3)
}
Ns <- lapply(x, N_fun)

power_means_fun <- function(x){
  mean(x$CTL_DS)
}
power_score <- lapply(x, power_means_fun)
x$Ukraine$CTL_DS

test <- 
  cbind.data.frame(
     round(do.call(rbind, symbolic_means),digits=2)
    ,round(do.call(rbind, symbolic_sds),digits=2)
    ,round(do.call(rbind, power_score),digits=2)
    ,round(do.call(rbind, Ns),digits=2)
    )

test <- `colnames<-`(test, c("symbolic_means","symbolic_sds","power_score", "Ns"))
test$iso2c <- rownames(test)
#autocoup_df$iso2c <- countrycode(test$country, "country.name", "iso2c")
# test$iso2c <- countrycode(test$country, "country.name", "iso2c")
# test$iso2c <- tolower(test$iso2c)
test$country <- countrycode(test$iso2c, "iso2c", "country.name")

test
```

h1 <- .3
w1 <- .5
s1 <- 18

lm_fit_intercept <- lm(moral_identity_symbolic ~ CTL_DS, data = df)

lm_fit <- lm(moral_identity_symbolic ~
                    # sex3
                    # + age
                     Power.Distance
                    + Individualism
                    + Masculinity
                    + Uncertainty.Avoidance
                    + Long.Term.Orientation
                    + Indulgence
                    + CTL_DG
                    + CTL_DS
                    + CTL_C
                , data = df
            )

lm_fit$coefficients[1]
lm_fit$coefficients[2]

g1 <- ggplot(test, aes(power_score
                       ,symbolic_means
                       ,country=iso2c
                       #,size=Ns
))+
  geom_abline(slope=lm_fit_intercept$coefficients[2],
              #slope=lm_fit$coefficients[9],
              intercept=lm_fit_intercept$coefficients[1],
              color="darkgrey",
              size=.5)+
  #geom_point(size=13,color="black")+
  geom_flag(
    position=position_jitter(
      h = h1
      , w = w1
      , seed = s1)
    #aes(power_score,symbolic_means,country = iso2c#, size=1#(Ns)
    #)
    ,size=7.5
  )+
  scale_country()+
  #scale_size(range = c(8,10))+
  geom_text(aes(power_score,symbolic_means),label=test$country
            ,vjust=3.8
            ,hjust=.44
            #,nudge_x = .03
            ,size = 1.6
            #,check_overlap = TRUE
            ,position = position_jitter(
              h = h1
              , w = w1
              , seed = s1
            )
  )+
  xlab("Tightness: Domain Specific")+
  ylab("Symbolization")+
  scale_y_continuous(expand = c(0, 0), limits = c(0, 10))+
  theme_bw() +
  theme(panel.border = element_blank(),
        axis.line = element_line(size = .2),
        strip.background  = element_blank(),
        #panel.grid = element_blank(),
        plot.title=element_text(#family="Times",
          size=12
        ),
        #legend.position="right",
        legend.text=element_text(#family="Times",
          size=8
        ),
        legend.title=element_text(#family="Times",
          size=10
        ),
        axis.text=element_text(#family="Times",
          colour = "black",
          size=8
        ),
        axis.ticks.x = element_blank(),
        axis.title=element_text(#family="Times",
          size=12
        ),
        strip.text=element_text(#family = "Times",
          size = 12
        ),
        # strip.background = element_rect(fill = "white"),
        legend.position="none")

ggsave("plots/ct_ds_symbolization.png", g1, width = 10, height = 6, units = "in", dpi = 300)

```

```{r, SymbolizationTDS,fig.cap="Relationship between Domain Specific Tightness and Symbolization",include=TRUE}
suppressWarnings(print(g1))

```

## Tightness Combination

```{r}
x <- df
x$CTL_C
x <- x[which(is.na(x$CTL_C)==FALSE),]

x$ISO2 <- countrycode(x$ISO3, "iso3c", "iso2c")
x$iso2 <- tolower(x$ISO2)

x <- x %>% group_by(iso2) %>% do(data = (.)) %>% with( set_names(data, iso2) )

means_fun <- function(x){
  mean(x$moral_identity_symbolic,na.rm = T)
}
symbolic_means <- lapply(x, means_fun)
sd_fun <- function(x){
  sd(x$moral_identity_symbolic,na.rm = T)
}
symbolic_sds <- lapply(x, sd_fun)
N_fun <- function(x){
  length(x$sex3)
}
Ns <- lapply(x, N_fun)

power_means_fun <- function(x){
  mean(x$CTL_C)
}
power_score <- lapply(x, power_means_fun)
x$Ukraine$CTL_C

test <- 
  cbind.data.frame(
     round(do.call(rbind, symbolic_means),digits=2)
    ,round(do.call(rbind, symbolic_sds),digits=2)
    ,round(do.call(rbind, power_score),digits=2)
    ,round(do.call(rbind, Ns),digits=2)
    )

test <- `colnames<-`(test, c("symbolic_means","symbolic_sds","power_score", "Ns"))
test$iso2c <- rownames(test)
#autocoup_df$iso2c <- countrycode(test$country, "country.name", "iso2c")
# test$iso2c <- countrycode(test$country, "country.name", "iso2c")
# test$iso2c <- tolower(test$iso2c)
test$country <- countrycode(test$iso2c, "iso2c", "country.name")

test
```

h1 <- .3
w1 <- .5
s1 <- 18

lm_fit_intercept <- lm(moral_identity_symbolic ~ CTL_C, data = df)

lm_fit <- lm(moral_identity_symbolic ~
                    # sex3
                    # + age
                     Power.Distance
                    + Individualism
                    + Masculinity
                    + Uncertainty.Avoidance
                    + Long.Term.Orientation
                    + Indulgence
                    + CTL_DG
                    + CTL_DS
                    + CTL_C
                , data = df
            )

lm_fit$coefficients[1]
lm_fit$coefficients[2]
